Particle-in-Cell modelling of synchrotron emission from relativistic supernovae

### 2020-04-10 papers/Physica2020/Romansky_Physica2020.tex
approx works for 90 turb

\begin{document}
\title{Modelling of electron acceleration in relativistic supernovae}

@@

Shock wave is initialized by an electron-proton plasma which is flowing into the simulation region through the right boundary and then reflecting from 
the super-conducting wall at the left boundary. We use the following parameters for the setups: the initial flow Lorentz factor $\gamma = 1.5$, magnetization $\sigma = \frac{B^2}{4\pi\gamma (n_p m_p + n_e m_e) c^2} = 0.04$ (in the turbulent case $B^2$ is the mean square field). The dimensionless thermal energy $\Delta \gamma = \frac{k T}{m_p c^2}$ is equal $10^{-4}$ and the proton mass is reduced to $m_p = 25 m_e$. Size of the simulation region along x axis is $L_x = 8000\frac{c}{\omega_p}$ and in transverse direction $L_y = 200\frac{c}{\omega_p}$, where $\omega_p$ is the plasma frequency $\omega_p = \sqrt{\frac{4\pi q^2 n}{\gamma m_e}}$. These sizes correspond to $80000$ and $2000$ grid points respectively. Also, $2000$ grid points correspond to approximately $10$ gyroradii of upstream protons.
We initialized turbulent field model by the following equation: 
\begin{equation}\label{field}
B_{turb} (\textbf{r}) = \sum_{\textbf{k}}\sum_{p=1,2}B(\textbf{k}) \textbf{e}_{p} sin(\textbf{k}\textbf{r}  + \phi (\textbf{k},p))
\end{equation}
where $B(k_x(i),k_y(j))$ is the amplitude of turbulent mode, usually we choose $B \propto k^{-11/6}$ to imitate Kolmogorov's spectrum, where $B^2 k^2 \propto k^{-5/3}$. $B$ is normalized to fixed fraction of total magnetic energy $\eta$. In further research with more wide spectrum of turbulence, it's behaviour may be important. $\textbf{e}_{p}$ are vectors perpendicular to wavevector $\textbf{k}$ corresponding to two different field polarizations and $\phi (i,j,p)$ is randomly generated phase for each mode. Wavevectors $\textbf{k}$ are distributed on a uniform grid, $k_x = i \Delta k, k_y = j \Delta k$ and $\Delta k \approx \frac{2 \pi}{10 r_g}$ where $r_g$ is upstream proton gyroradius. The maximum wavevector $k_{max} \approx \frac{2 \pi}{r_g}$. These equations (\ref{field}) are evaluated in the plasma rest frame and then magnetic field is transformed to the downstream frame. Regular magnetic field is perpendicular to the plane of simulation. Such turbulent field structure is similar to so-called 2d-turbulence which is observed in solar wind\cite{Matthaeus1990}. Density and velocity of plasma flow is uniform and the electric field is set to compensate Lorentz force in every point.

@@

@@

\begin{figure}[h!]
		\centering
		\includegraphics[width=0.7\textwidth]{fig/regular_field.eps} 
		\caption{Magnetic field in shock wave without turbulence.}
		\label{regularB}
\end{figure}
\begin{figure}[h!]
		\centering
		\includegraphics[width=0.7\textwidth]{fig/turbulent_field.eps} 
		\caption{Magnetic field in shock wave with 90\% turbulence.}
		\label{turbulentB}
\end{figure}
The spectrum of accelerated electrons  shown in Figure \ref{spectrum}  demonstrated a strong dependence on the fraction of the turbulent magnetic 
field energy density in the wind. 
When a half of the magnetic field energy density is in the magnetic turbulence the particle spectrum becomes significantly 
different from the spectrum in a homogeneous field. A fraction of the accelerated electrons highly increases with the growth of turbulent energy fraction. 
The quantity which is showing how much of the upstream flow kinetic energy (or the ram pressure) goes to the accelerated electrons 
$\epsilon_e$ can be defined as that in \cite{Crumley2019}
\begin{equation}
\epsilon_e = \frac{\int_{p_{inj}}^{\infty}E(p)F(p)dp}{\int_{0}^{\infty}E(p)F(p)dp }\frac{m_e(\langle \gamma \rangle - 1)}{m_p (\gamma_0 - 1)}
\end{equation}
where $F(p)$ is the electron distribution function, $E(p)$ is the energy of a particle of momentum $p$ and $\langle \gamma \rangle$ is the averaged Lorentz-factor. 
$p_{inj}$ is injection momentum, showing that particle is non-thermal and we consider it equal to $2 \gamma_0 \beta_0 m_p c$. For simulation with the strongest turbulence, $\epsilon_e$ is equal to $2\cdot10^{-3}$, and it is several times higher then that in a quasi-parallel shock wave.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{fig/spectrum.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different turbulence fractions.}
	\label{spectrum}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{fig/spectrum_length.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different turbulence length, turbulence energy fraction is 90\%.}
	\label{spectrum_length}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{fig/electrons_mass.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different mass relation, turbulence energy fraction is 90\%.}
	\label{electrons_mass}
\end{figure}

>>>>

\begin{document}
\title{Particle-in-Cell modelling of synchrotron emission from relativistic supernovae}

@@

Shock wave is initialized by an electron-proton plasma which is flowing into the simulation region through the right boundary and then reflecting from 
the super-conducting wall at the left boundary. We use the following parameters for the setups: the initial flow Lorentz factor $\gamma = 1.5$, magnetization $\sigma = \frac{B^2}{4\pi\gamma (n_p m_p + n_e m_e) c^2} = 0.04$ (in the turbulent case $B^2$ is the mean square field). The dimensionless thermal energy $\Delta \gamma = \frac{k T}{m_p c^2}$ is equal $10^{-4}$ and the proton mass is reduced to $m_p = 100 m_e$. Size of the simulation region along x axis is $L_x = 30000\frac{c}{\omega_p}$ and in transverse direction $L_y = 400\frac{c}{\omega_p}$, where $\omega_p$ is the plasma frequency $\omega_p = \sqrt{\frac{4\pi q^2 n}{\gamma m_e}}$. These sizes correspond to $150000$ and $2000$ grid points respectively. Also, $2000$ grid points correspond to approximately $10$ gyroradii of upstream protons.
We initialized turbulent field model by the following equation: 
\begin{equation}\label{field}
B_{turb} (\textbf{r}) = \sum_{\textbf{k}}\sum_{p=1,2}B(\textbf{k}) \textbf{e}_{p} sin(\textbf{k}\textbf{r}  + \phi (\textbf{k},p))
\end{equation}
where $B(k_x(i),k_y(j))$ is the amplitude of turbulent mode, usually we choose $B \propto k^{-11/6}$ to imitate Kolmogorov's spectrum, where $B^2 k^2 \propto k^{-5/3}$. $B$ is normalized to fixed fraction of total magnetic energy $\eta$. In further research with more wide spectrum of turbulence, it's behaviour may be important. $\textbf{e}_{p}$ are vectors perpendicular to wavevector $\textbf{k}$ corresponding to two different field polarizations and $\phi (i,j,p)$ is randomly generated phase for each mode. Wavevectors $\textbf{k}$ are distributed on a uniform grid, $k_x = i \Delta k, k_y = j \Delta k$ and $\Delta k \approx \frac{2 \pi}{10 r_g}$ where $r_g$ is upstream proton gyroradius. The maximum wavevector $k_{max} \approx \frac{2 \pi}{r_g}$. These equations (\ref{field}) are evaluated in the plasma rest frame and then magnetic field is transformed to the downstream frame. Regular magnetic field is perpendicular to the plane of simulation. Such turbulent field structure is similar to so-called 2d-turbulence which is observed in solar wind\cite{Matthaeus1990}. Density and velocity of plasma flow is uniform and the electric field is set to compensate Lorentz force in every point.

@@

\section{Synchrotron spectrum evaluation}
We evaluate spectrum of synchrotron emission using standart formula \cite{Syrovatsky} and take into account self-absorption\cite{Ghisellini1991}. Emissivity at the frequency $\nu$ of unit volume is given by
\begin{equation}\label{emissivity}
I_{\nu}={\int_{m_e c^2}^{\infty}}\frac{\sqrt{3} e^3}{m_e c^2}B_{\perp}F_e(E)\frac{\nu}{{\nu}_c}{\int_{\frac{\nu}{{\nu}_c}}^{\infty}}K_{\frac{5}{3}}({\eta})d{\eta} dE
\end{equation}
Where $B_{\perp}$ is component of magnetic field, normal to the observer direction, $F_e(E)$ is electrons' distribution function, normalized on concentration, ${\nu}_c$ is critical frequency defined as $\frac{3 e B_{\perp}}{4 \pi {\gamma}^2 m_e c}$, $\gamma$ is Lorentz-factor and $K_{\frac{5}{3}}$ is modified Bessel function of second kind.

Self-absorption cross-section is defined as
\begin{equation}\label{selfabsorption}
{\sigma}(\nu, \gamma) = \frac{16 \pi^2}{3\sqrt{3}}\frac{e}{B_{\perp}}\frac{1}{\gamma^5}K_{\frac{5}{3}}(\frac{\nu}{{\nu}_c})
\end{equation}

@@

\begin{figure}[h!]
		\centering
		%\includegraphics[width=0.7\textwidth]{fig/regular_field.eps} 
		\caption{Magnetic field in shock wave without turbulence.}
		\label{regularB}
\end{figure}
\begin{figure}[h!]
		\centering
		%\includegraphics[width=0.7\textwidth]{fig/turbulent_field.eps} 
		\caption{Magnetic field in shock wave with 90\% turbulence.}
		\label{turbulentB}
\end{figure}
The spectrum of accelerated electrons  shown in Figure \ref{spectrum}  demonstrated a strong dependence on the fraction of the turbulent magnetic 
field energy density in the wind. 
When a half of the magnetic field energy density is in the magnetic turbulence the particle spectrum becomes significantly 
different from the spectrum in a homogeneous field. A fraction of the accelerated electrons highly increases with the growth of turbulent energy fraction. 
The quantity which is showing how much of the upstream flow kinetic energy (or the ram pressure) goes to the accelerated electrons 
$\epsilon_e$ can be defined as that in \cite{Crumley2019}
\begin{equation}
\epsilon_e = \frac{\int_{p_{inj}}^{\infty}E(p)F(p)dp}{\int_{0}^{\infty}E(p)F(p)dp }\frac{m_e(\langle \gamma \rangle - 1)}{m_p (\gamma_0 - 1)}
\end{equation}
where $F(p)$ is the electron distribution function, $E(p)$ is the energy of a particle of momentum $p$ and $\langle \gamma \rangle$ is the averaged Lorentz-factor. 
$p_{inj}$ is injection momentum, showing that particle is non-thermal and we consider it equal to $2 \gamma_0 \beta_0 m_p c$. For simulation with the strongest turbulence, $\epsilon_e$ is equal to $2\cdot10^{-3}$, and it is several times higher then that in a quasi-parallel shock wave.
\begin{figure}[h!]
	\centering
	%\includegraphics[width=0.7\textwidth]{fig/spectrum.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different turbulence fractions.}
	\label{spectrum}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	%\includegraphics[width=0.7\textwidth]{fig/spectrum_length.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different turbulence length, turbulence energy fraction is 90\%.}
	\label{spectrum_length}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	%\includegraphics[width=0.7\textwidth]{fig/electrons_mass.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different mass relation, turbulence energy fraction is 90\%.}
	\label{electrons_mass}
\end{figure}
